LaTex Paper Writing Tips for Beginners

### 2021-11-19 paper_writing_tips.tex
Add figures

\section{Suggestions}
\begin{itemize}
    \item use newcommand for abbr
    \item Fig/Tab.
    \item use newcommand in equation
    \item Principal: be compact and clear.
    \item Contributions
\end{itemize}

@@

\clearpage
\section{Sample layout for tables}
Suggestions.
\begin{itemize}
    \item The caption should be at the top of the table.
    \item The text should not be too small.
    \item 
\end{itemize}

% single column
\input{tables/table1}
\input{tables/table2}
\input{tables/table3}
\input{tables/table4}
\input{tables/table5}
\input{tables/table6}
\input{tables/table_network2}

\input{tables/table_figure1}

% two column
\input{tables/table8}
\input{tables/table9}
\input{tables/table7}
\input{tables/table_figure2}

\input{tables/table_network1}

>>>>

\section{Suggestions}
\begin{itemize}
    \item use newcommand for abbr
    \item Fig/Tab.
    \item use newcommand in equation
    \item Principal: be compact and clear.
    \item Contributions
    \item Use Figure x at the beginning of the sentence, and Fig.~x else where.
    \item Also use Table~x when referring table.
\end{itemize}

\clearpage
\section{Sample layout for tables}
Suggestions.
\begin{itemize}
    \item The caption should be at the top of the table.
    \item The text should not be too small.
    \item It is better to put the table at top of the paper.
\end{itemize}

% single column
\input{tables/table1} % simple table
\input{tables/table2} % multi-column table
\input{tables/table3} % multi-column with makecell
\input{tables/table4} % multi-column with vertical lines
\input{tables/table5} % multi-column with bold font
\input{tables/table6} % multi-column with parallel lines
\input{tables/table_network2} % single-column network arch

\input{tables/table_figure1} % table with images

% two column
\input{tables/table8} % two-column table
\input{tables/table9} % two-column table with color header
\input{tables/table7} % two-column table with two sub-tables
\input{tables/table_figure2} % two-column tables with images in the header

\input{tables/table_network1} % two column network arch table

@@

% Single-column
\input{figures/figure1} % single image
\input{figures/figure2} % two images
\input{figures/figure3} % four images
\input{figures/figure4} % four images with text header
\input{figures/figure5} % four images with vertical text
\input{figures/figure6} % two sub figures

% Two column
\input{figures/figure7} % single image
\input{figures/figure8} % multiple images
\input{figures/figure9} % 
\input{figures/figure10} % 
\input{figures/figure11} %
